---
title: "Project 1"
author: "Khalil Albattashi"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: show
    csl: biomed-central.csl
    df_print: paged
    fig_caption: yes
    fig_height: 6
    fig_width: 7
    number_sections: yes
    theme: journal
    toc: yes
    toc_float: yes
    word_document:
      toc: yes
      toc_depth: '4'
      pdf_document:
      df_print: kable
      fig_caption: yes
      fig_height: 6
      fig_width: 7
      highlight: tango

#bibliography: project.bib
abstract: This Project analysis the methods used to detect defects within NASA software code. Four methods were used including lines of code, cycloclamatic complexity, Essential Complexity, and Design Complexity. the methods were analyzed using probabilities  for accuracy, detection rate, false alarm rate, and precision. the most effective of the methods showed to be lines of code
---


---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction to the data

## Data and variables(see MS pg. 77,125)
The problem is assigning different methods to detect defects in software code in NASA instruments. the data in SWDETECTS contains models that were evaluated "true" and "false" in terms of defects  

## Summary Table 
```{r}
library(data.table)
data = data.table(
  id = c("", "Algorithm","Predicts", "Defects" ),
  a = c("", "No", "Yes", ""),
  b = c("False", "a", "c", ""),
  c = c("True", "b", "d", "")
)
data
```



### Make formulae 

Using $\LaTeX$ construct the formulae for 

$$
\begin{eqnarray}
\ Accurecy:&  \ P(Algorithm \ is \  correct) = & \frac {(a + b)}{(a + b + c + d)}
\end{eqnarray}
$$
$$
\begin{eqnarray}
\ Detection\ rate :  \ P(predict \  defect \ | \  module \ has \  defect)& = & \frac {(d)}{(b + d)}
\end{eqnarray}
$$
$$
\begin{eqnarray}
\ False \ alarm \ rate : \ P(predict \  defect \ | \  module \ has \  no \ defect) & = & \frac {(c)}{(a + c)}
\end{eqnarray}
$$
$$
\begin{eqnarray}
\ Precision \ P(model \ has  \  defect \ | \  predict \  defect)& = & \frac {(d)}{(c + d)}
\end{eqnarray}
$$

# R functions
Using the above definitions make R functions that will create the required probabilities, please remove `eval=FALSE` when creating the functions :

```{r accuracy, eval=FALSE}
acc=function(a,b,c,d)
{
  (a + b)/(a + b + c + d)
}
```

```{r detecton, eval=FALSE}
detect=function(b,d)
{
  d / (b + d)
}
```

```{r alarm, eval=FALSE}
falarm=function(a,c)
{
  c / (a + c)
}
```

```{r precision, eval=FALSE}
prec=function(c,d)
{
  d / (c + d)
}
```


# Create the tables in Figure SIA3.1

the first table and barplot provides the values for LOC > 50 which shows the probability of LOC predictor

```{r }
swd=read.csv("swdefects.csv")
head(swd)

```
```{r}
tab=with(swd, table(predict.loc.50,defect))
barplot(tab, beside=TRUE, leg=TRUE)

tab2=addmargins(tab)
tab2
```
```{r}
tab=with(swd, table(predict.vg.10,defect))
barplot(tab, beside=TRUE, leg=TRUE)

tab3=addmargins(tab)
tab3
```
```{r}
tab=with(swd, table(predict.evg.14.5,defect))
barplot(tab, beside=TRUE, leg=TRUE)

tab4=addmargins(tab)
tab4
```
```{r}
tab=with(swd, table(predict.ivg.9.2,defect))
barplot(tab, beside=TRUE, leg=TRUE)

tab3=addmargins(tab)
tab3
```








# Create the corrected table on page 127 (there are mistakes in it), TABLE SIA3.3

```{r}
acc=function(a,b,c,d)
{
  (a + b)/(a + b + c + d)
}

detect=function(b,d)
{
  d / (b + d)
}

falarm=function(a,c)
{
  c / (a + c)
}

prec=function(c,d)
{
  d / (c + d)
}

accloc = acc(400, 29, 49, 20)
detectloc = detect(29, 20)
falarmloc= falarm(400, 49)
precloc = prec(49, 20)

accvg = acc(397, 35, 52, 14)
detectvg = detect(35, 14)
falarmvg = falarm(397, 52)
precvg = prec(52, 14)

accevg = acc(441, 47, 8, 2)
detectevg = detect(47, 2)
falarmevg = falarm(441, 8)
predevg = prec(8, 2)

accivg = acc(422, 38, 27, 11)
detectivg = detect(38, 11)
falarmivg = falarm(422, 27)
predivg = prec(27, 11)

tab3 = matrix(round(c(accloc, accvg, accevg, accivg, detectloc, detectvg, detectevg, detectivg, falarmloc, falarmvg, falarmevg, falarmivg, precloc, precvg, predevg, predivg), 3), ncol = 4, byrow= FALSE)

rownames(tab3) = (c("Lines of Code", "Cycloclamatic Complexity", "Esseintial Complexity", "Design Complexity"))

colnames(tab3) = (c("Accuracy", "Detection Rate", "False Alarm Rate", "Precision"))

tab3 = as.table(tab3)
tab3
```

```{r}
mybar = function(tab, dec){
  barplot(tab, dec, beside = TRUE, leg = TRUE, col = rainbow(4))
  return (list(tab, round(dec)))
}
mybar(tab=tab3, dec = 4)
```


    


